\emph{Light Exposure Behavior Assessment (LEBA)}: Long and Short Form

### 2021-10-12 manuscript.Rmd
EFA Plot direction

```{r EFAplotcode, include=FALSE}
#library(DiagrammeR)
EFAplot <- grViz("
digraph boxes_and_circles {

@@

# node definitions with substituted label text
node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
fixedsize = true, fontsize = 35]
F1 [label = 'F1']
F2 [label = 'F2']
F3 [label = 'F3']
F4 [label = 'F4']
F5 [label = 'F5']
node [fontname = Helvetica, shape = box]
b [label = 'item16']
c [label = 'item36']
d [label = 'item17']
e [label = 'item11']
f [label = 'item10']
g [label = 'item12']
h [label = 'item7']
i [label = 'item8']
j [label = 'item9']
k [label = 'item27']
l [label = 'item3']
m [label = 'item40']
n [label = 'item30']
o [label = 'item41']
p [label = 'item33']
q [label = 'item32']
r [label = 'item35']
s [label = 'item37']
t [label = 'item38']
u [label = 'item46']
v [label = 'item45']
w [label = 'item25']
x [label = 'item4']
y [label = 'item1']
z [label = 'item26']

{rank = same; F1 F2 F3 F4 F5}
# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 35]
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
F2 -> e [label = '0.79']
F2 -> f[label = '0.76']
F2 -> g [label = '0.65']
F2 -> h[ label = '0.50']
F2 -> i [label = '-.49',color =red]
F2 -> j [label = '0.32']
F3 -> k [label = '0.80']
F3 -> l [label = '0.80']
F3 -> m [label = '0.65']
F3 -> n [label = '0.49']
F3 -> o [label = '36']
F4 -> p [label = '0.74']
F4 -> q [label = '0.73']
F4 -> r [label = '0.66']
F4 -> s [label = '-0.39', color =red]
F4 -> t [label = '0.39']
F5 -> u [label = '0.60']
F5 -> v [label = '0.59']
F5 -> w [label = '0.41']
F5 -> x [label = '0.41']
F5 -> y [label = '0.40']
F5 -> z [label = '0.35']
}
")

>>>>

```{r EFAplotcode, include=FALSE}

EFAplot <- grViz("
digraph boxes_and_circles {

@@

# node definitions with substituted label text
node [fontname = Helvetica, shape = circle,  margin = 0.5, width = 3.5, height = .5,
fixedsize = true, fontsize = 35]
F5 [label = 'F5']
F4 [label = 'F4']
F3 [label = 'F3']
F2 [label = 'F2']
F1 [label = 'F1']

node [fontname = Helvetica, shape = box]
b [label = 'item16']
c [label = 'item36']
d [label = 'item17']
e [label = 'item11']
f [label = 'item10']
g [label = 'item12']
h [label = 'item7']
i [label = 'item8']
j [label = 'item9']
k [label = 'item27']
l [label = 'item3']
m [label = 'item40']
n [label = 'item30']
o [label = 'item41']
p [label = 'item33']
q [label = 'item32']
r [label = 'item35']
s [label = 'item37']
t [label = 'item38']
u [label = 'item46']
v [label = 'item45']
w [label = 'item25']
x [label = 'item4']
y [label = 'item1']
z [label = 'item26']

{rank = same; F1 F2 F3 F4 F5}
# edge definitions with the node IDs
edge [fontname = Helvetica, fontsize = 35]
F5 -> u [label = '0.60']
F5 -> v [label = '0.59']
F5 -> w [label = '0.41']
F5 -> x [label = '0.41']
F5 -> y [label = '0.40']
F5 -> z [label = '0.35']
F4 -> p [label = '0.74']
F4 -> q [label = '0.73']
F4 -> r [label = '0.66']
F4 -> s [label = '-0.39', color =red]
F4 -> t [label = '0.39']
F3 -> k [label = '0.80']
F3 -> l [label = '0.80']
F3 -> m [label = '0.65']
F3 -> n [label = '0.49']
F3 -> o [label = '36']
F2 -> e [label = '0.79']
F2 -> f[label = '0.76']
F2 -> g [label = '0.65']
F2 -> h[ label = '0.50']
F2 -> i [label = '-.49',color =red]
F2 -> j [label = '0.32']
F1 -> b[label = '0.99']
F1-> c [label = '0.93']
F1-> d [label = '0.80']
}
")
